---
title: "Project"
author: Mohamed, Rayan and Jasmine
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---


```{r}
#knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```

```{r}
# Load libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
```
 > What shapes people’s opinion on climate change?
 (look at party affiliation, age, fed_sci_budget, science_is_honest)


```{r}
 # Load data
raw_survey_data <- read.csv("https://www.macalester.edu/~ajohns24/data/pulse_of_the_nation.csv")

names(raw_survey_data) <- c("income", "gender", "age", "party", "trump_approval", "education", "marital", "robots", "climate_change", "transformers", "science_is_honest", "vaccines_are_safe", "books", "ghosts", "fed_sci_budget", "earth_sun", "wise_unwise")

raw_survey_data <- raw_survey_data %>% 
  mutate(climate_change_binary = (climate_change == "Real and Caused by People"))
```

### Party affiliation vs Climate Change
```{r}
raw_survey_data %>%
  group_by(climate_change_binary, party) %>% 
  summarise(num_of_ind = n()) %>% 
  ggplot(aes( y= num_of_ind, x = party, fill = climate_change_binary)) +
  geom_col() 



```



### age vs Climate Change 


```{r}
raw_survey_data %>% 
  ggplot(aes(y = age, x = climate_change_binary))+
  geom_boxplot()
```

> From the boxplot above, younger individuals tend to believe that climate change is real and is caused by people more than the older individuals.



### age vs Climate Change vs science_is_honest

```{r}
raw_survey_data %>% 
  ggplot(aes(y = age, x = climate_change_binary, fill = science_is_honest))+
  geom_boxplot() +
  labs(title = "Do age and belief in science affect views on climate change?", x = "Climate change is real and caused by people", y= "Age")
```
> People who strongly agree with the statement that science is real also believe that climate change is real




\
\



## Part 1: Introduction


> Cards Against Humanity’s “Pulse of the Nation” project conducted monthly polls into people’s social views, political views, and other things.We will use data from their survey conducted September 15-30, 2017 to explore how various factors can affect people’s belief in climate change.


```{r} 
# Number of people in the dataset 
nrow(raw_survey_data)

# Number of people in each party 
raw_survey_data %>%
  group_by(party) %>% 
  summarise(num_of_ind = n()) 
```


> We can see from the calculations above that the number of people who don't identify as a democrat or a republican is high (368). The are also more individuals who identify as democrats (274) than republicans (208)

\
\
\
\
\
\



## Part 2: Analysis


\
\
\
\
\
\



## Part 3: Collaboration


